External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-29 CVPR2017_Review_Unified.tex
add

\begin{table*}
\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\label{tab2}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
%\\
%\hline
%SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
\\
\hline
\end{tabular}
\end{center}\vspace{-5mm}
\end{table*}

@@

In this section, we compare the proposed method  with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}. These methods are designed for removing Gaussian noise. For BM3D and WNNM, the level $\sigma$ of Gaussian noise is very important and is estimated by the method \cite{noiselevel}. The other parameters are set as default. For the methods of MLP, CSF, and TRD, we employ their default paramters settings. Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels seperately for color noisy images. We also compare with three other denoising methods \cite{noiseclinic,neatimage,crosschannel2016}. The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior for image denoising. The Neat Image (NI) is a commercial software on image denoising and is embeded into Photoshop and Corel PaintShop Pro \cite{neatimage}. The recently proposed method Cross-Channel (CC) \cite{crosschannel2016} is a state-of-the-art method for real image denoising problem. The comparison is performed on the two datasets mentioned above.

For the first dataset, the average PSNR values on the 60 images cropped from \cite{crosschannel2016} are listed in Table \ref{tab2}. The number in red color and blue color means the best and second best results, respectively. It can be seen that our proposed method achieves the best PSNR results than other methods and the gap over the second best result (blue) is 1dB. Considering that the 60 cropped images contain different scenes with complex noise, the improvements of our proposed method is impressed. Besides, to compare with the recently proposed \cite{crosschannel2016}, we also perform experiments on the 15 images used in \cite{crosschannel2016}. The comparison  on PSNR values are listed in Table \ref{tab3}. As we can see, our proposed method obtains best PSNR values on most (9 out of 15) of the images captured by different camera settings. Noted that, though the method \cite{crosschannel2016} trains a specific model for each camera settng, our proposed general method still gains 0.28dB improvements over \cite{crosschannel2016}. We also compare the visual quality of the compared method. For example, Figure \ref{fig5} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO$=3200$. More visual comparisons can be found in the supplementary file. We can see that BM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts while MLP, TRD are likely to over-smooth the image. Our proposed method preserves edges and textures much better than other methods.

For the second dataset provided in \cite{ncwebsite}, we can only compare the visual quality of the images denoised by different methods. In Figure \ref{fig6}, we take the real noisy image "Dog" as an example and more visual comparisons can be found in the supplementary file. It can be seen that the methods of BM3D, WNNM would over-smooth the whole image while remain some noise in local areas. The methods of MLP, TRD also remain a lot of noise in the whole image. This demonstrates that the methods designed for Gaussian noise are not suitable for the complex noise in real noisy images. Even Noise Clinic and Neat Image, which are specifically developed for real noisy images, would sometimes fail to deal with the complex noise in real noisy images. However, we can see that the proposed algorithm recoveries more faithfully the fine structures of the eye area than the other competing methods.

In summary, our proposed algorithm demonstrates impressing ability on dealing with the complex noise in real noisy images in terms of PSNR and visual quality.

>>>>

\begin{table*}
\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\label{tab2}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
%\\
%\hline
%SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
\\
\hline
\end{tabular}
\end{center}\vspace{-4mm}
\end{table*}

@@

In this section, we compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}. These methods are designed for removing Gaussian noise. For BM3D and WNNM, the level $\sigma$ of Gaussian noise is very important and is estimated by the method \cite{noiselevel}. The other parameters are set as default. For the methods of MLP, CSF, and TRD, we employ their default paramters settings. Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels seperately for color noisy images. The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior. The recently proposed Cross-Channel (CC) \cite{crosschannel2016} is a state-of-the-art method on real image denoising problem. We also compare with Neat Image (NI), a commercial software for image denoising. Due to its excellant performance, NI is embeded into Photoshop and Corel PaintShop Pro \cite{neatimage}.

The comparisons are performed on the two datasets mentioned before. For the first dataset \cite{crosschannel2016}, the average PSNR results on the 60 cropped images  are listed in Table \ref{tab2} (the code of \cite{crosschannel2016} is not available so that it is not compared). The numbers in red color and blue color are the best and second best results, respectively. It can be seen that our proposed method achieves much better PSNR results than the other methods. The improvement of our method over the second best method (\textbf{TRD}) is 1dB. To compare with \cite{crosschannel2016}, we also perform experiments on the 15 cropped images used in \cite{crosschannel2016}. The PSNR values are listed in Table \ref{tab3}. As we can see, on most (9 out of the 15) images captured by different cameras and camera settings, our proposed method obtains better PSNR values than the other methods. Noted that, though in \cite{crosschannel2016} a specific model is trained for each camera and camera setting, our proposed general method still gains 0.28dB improvements on PNSR over \cite{crosschannel2016}. We also compare the visual quality of the denoised images by the competing methods. Figure \ref{fig5} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO $=3200$ by the competing methods. More visual comparisons can be found in the supplementary file. We can see that BM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TRD are likely to over-smooth the image. Owe to the unify of external and internal priors, our proposed method preserves edges and textures better than other methods.

For the second dataset \cite{ncwebsite} with no "ground truth" images, we only compare the visual quality of the denoised images. Figure \ref{fig6} shows the denoised images of "Dog" by the competing methods. More visual comparisons can be found in the supplementary file. It can be seen that the methods of BM3D, WNNM tend to globally over-smooth the image while locally remain some noise, while the methods of MLP, TRD are likely to remain noise in the whole image. This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images. Though Noise Clinic and Neat Image are specificly developed for removing complex noise, they would sometimes fail to recovery real noisy images. However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.

In summary, our proposed method demonstrates impressing ability on dealing with the complex noise in real noisy images in terms of PSNR and visual quality.
